---
title: "Aides Drug"
author: "Taylor Stohl"
date: "Summer 2021"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
triUmp <-read.csv(file="triUmpsal.csv",header=TRUE)
females = filter(triUmp, gender =="F")
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative aides drug (triUmpsal) is under test in clinical trials. Consider only the females, does this drug seem effective?  Hint - use dplyr to obtain that subpopulation with the filter command.

#Introduction:

In this project, the goal is to show the results of the new preventative aids drug called triUmpsal in ONLY the females. The first step is to decide what helper file to use. Since treatment and infected are both categorical data, the Cat~Cat helper file is used. Next, the data has to be adjusted to only select the female subset. To only select the females from the triUmp data set, a dplyr code was implemented to specifically select this data. Also, the data results need to be put into a percentage plot to make it easier to read. Line 11 is a code that inputs all data totaling 2173 results. Line 12 is the code to only select the females. This data contains only 11768 results, about half of the results found in triUmp. 

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->



# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
dd2 <- females %>% group_by(infected,treatment) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))


# the group_by followed by summarize(count=n())

basicC <- ggplot(dd2,aes(x=infected,y=count,fill=treatment))
basicC + geom_bar(stat="identity",position="dodge")

#Now for percentage plot

basicCC <- ggplot(dd2,aes(x=infected,y=prcnt*100,fill=treatment)) 
basicCC + geom_bar(stat="identity", position = "dodge")
```


There are two plots. In first plot,the x-axis represents infected, whether the participants were infected with aids or they were not. The y-axis represents the count, or number of people that got aids or didn't get aids. 

In the second plot, the one above, The The left two bars of the graph are all the people that got aids. The x-axis represents whether a person got aids or not. The y-axis, however, instead of representing the number of people who got aids, now represents the percentage of people that got aids after taking the the placebo or taking the drug triUmpsal.

The plot shows that a shocking 60% of people that took the drug got aids, while only 40% of the people that received the placebo got aids. The odds of getting aids while taking the drug is to 3:2. The drug appears to be  completely ineffective. The women who took the drug are one and half times more likely to get aids than women taking the placebo.


The codes that  create this plot start with the code block beginning with dd2. dd2 can be seen in the environment pane and if inspected contains 4 variables.These variables include infected, treatment, count, and prcent(stands for percent). The second group of codes is called the basicC. BasicC can also be seen in the environment pane and appears to contain a list of 9 variables. This information creates the first plot. The basicCC is the last bunch of codes and is also in the files pane. It also contains 9 variables and helps to create the percentage plot, the second plot.


### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
table1 <- xtabs(~infected + treatment, data=females)
rowPerc(table1)
colPerc(table1)
```


Among the women that got aids about 59% had taken the vaccine and about 41% had taken the placebo. The odds concluded in this table are  approximately 59 to 41. The odds of getting aids is about 59 to 41. This further proves how ineffective the drug is. Females who took the drug were about 18 percent more likely to get aids than those who only took the placebo.


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```
The p-value is 0.00006.596. This in an incredibly small number and with that being said, the conclusion is that these results are unlikely to occur by chance.

The Fishers's Exact Test illustrates that the odds ratio is 1.54.
Women who got the drug were about 1.54 times more likely to get aids than women that only took the placebo.

The null hypothesis is rejected in favor the the alternative. The drug is not effective in reducing the chances of getting aids in females.


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

The drug TriUmpsal was not effective in protecting women against contracting aids. The odds ratio turned out to be 1.54. Women that received the drug were 1.54 times more likely to get aids than women that only received the placebo. The p-value is a tiny number,  only 0.000596, which means that these results are very unlikely to occur by chance. Women who took the placebo were better off than those that took the drug triUmpsal.
This drug failed the clinical trial, it was found to not be effective.

 The Cat~Cat helper file was used to assist this project. A code to select only women from the triUmp data set was also used. 



